PODD Ontology Driven Database

### 2012-03-25 csiroala2012/Podd-20120402.tex
add csiro presentation based on hrppc presentation

\title{PODD Ontology Driven Database}
\author{Dr Peter Ansell}
\institute{University of Queensland}
\date{13 March 2012}

@@

\begin{itemize}
 \item PODD was designed by Yuan-Fang Li and Gavin Kennedy for the High Resolution Plant Phenomics Centre
 \item Implemented between 2009 and 2011
\end{itemize}

@@

\begin{frame}
\frametitle{Next steps}

\begin{itemize}
 \item Use upcoming SPARQL 1.1 Query and Update standards
 \item Support OWL-2
 \item Pure SPARQL access using a single database
 \item Support links from experiments to other RDF documents
\end{itemize}

>>>>

\title{PODD Ontology Driven Database}
\author{Dr Peter Ansell}
\institute{University of Queensland}
\date{2 April 2012}

@@

\begin{itemize}
 \item PODD was designed by Yuan-Fang Li and Gavin Kennedy
 \item Implemented between 2009 and 2011
\end{itemize}

@@

\begin{frame}
\frametitle{Redesign}

\begin{itemize}
 \item Use upcoming SPARQL 1.1 Query and Update standards
 \item Support OWL-2
 \item Pure SPARQL access using a single database, including for management information to enable unified queries
 \item Support links between objects in PODD
\end{itemize}
